---
title: "Eating Out"
author: "Omar Challan"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out. The variable name you are looking for is "eatout".
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


# Methods

Looking at my data and considering the problem question. We are comparing to categorical data types. Therefore, we will use the cat–cat helper file to answer the question in hand.  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(haven)
require(knitr)
require(foreign)
```
```{r, eval=TRUE, warning=FALSE}
GSS <-read_dta(file="GSS1996.dta")
GSS <- readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


# plots

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

From the previous data, we can see that the overall frequency of the white race to eat out is higher than the black, and the other races. The black race has the highest frequency for not eating out, compared to the white and the other races. All the other races represented in the above graph had a median statistics compared to the data from the white and the black races. 



# Numerical


```{r}
table1 <- xtabs(~race + eatout,data=mydata)
rowPerc(table1)
colPerc(table1)
```

The white race is eating at the percentage of 82.83%, the black race is eating at the percentage of 68.75, and the other races are eating at the percentage of 77.78%.

# Inferential

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

From the previous data, we noticed a statistical difference between the data. 

```{r}
fisherXY(mydata$race,mydata$eatout,printAll = TRUE)
```

When we first ran the Fisher XY commands we got a low p-value only between white and black. However, when we ran it the other time, after adding the print, all equal, true part, we got two different other values that were significantly higher than the first one. 




